---
title: "BPS Model Analysis Report"
author: "Generated from BPS Database"
date: "`r Sys.Date()`"
format: 
  html:
    theme: flatly
    toc: true
    toc-depth: 3
    code-fold: true
    fig-width: 10
    fig-height: 6
params:
  bps_model: "10080_1_2_3_7"
  db_host: "localhost"
  db_name: "bps_database"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load functions
source("bps_database_r_functions.R")

# Connect to database
con <- connect_bps_db(host = params$db_host, dbname = params$db_name)
```

# BPS Model: `r params$bps_model`

## Overview

This report provides a comprehensive analysis of BPS model `r params$bps_model` using data from the BPS database.

```{r data-loading}
# Load all data for this BPS model
bps_data <- get_bps_complete_data(con, params$bps_model)

# Display basic info
if (nrow(bps_data$indicators) > 0) {
  cat("Common Name:", bps_data$indicators$common_name[1], "\n")
  cat("Scientific Name:", bps_data$indicators$scientific_name[1], "\n")
}
```

## Species Indicators

```{r indicators-table}
if (nrow(bps_data$indicators) > 0) {
  knitr::kable(bps_data$indicators, 
               caption = "Species indicators for this BPS model")
} else {
  cat("No indicator data available")
}
```

## Fire Frequency Analysis

```{r fire-frequency}
if (nrow(bps_data$fire_frequency) > 0) {
  knitr::kable(bps_data$fire_frequency, 
               caption = "Fire frequency data")
  
  # Create visualization
  library(ggplot2)
  p <- ggplot(bps_data$fire_frequency, 
              aes(x = severity, y = return_intervaly_years)) +
    geom_col(fill = "steelblue") +
    labs(title = "Fire Return Intervals by Severity",
         x = "Fire Severity",
         y = "Return Interval (Years)") +
    theme_minimal()
  
  print(p)
} else {
  cat("No fire frequency data available")
}
```

## State Class Transitions

### Deterministic Transitions

```{r deterministic}
if (nrow(bps_data$deterministic) > 0) {
  knitr::kable(bps_data$deterministic, 
               caption = "Deterministic state class transitions")
} else {
  cat("No deterministic transition data available")
}
```

### Probabilistic Transitions

```{r probabilistic}
if (nrow(bps_data$probabilistic) > 0) {
  knitr::kable(bps_data$probabilistic, 
               caption = "Probabilistic state class transitions")
} else {
  cat("No probabilistic transition data available")
}
```

## Model Information

### Modelers and Reviewers

```{r modelers}
if (nrow(bps_data$modelers) > 0) {
  knitr::kable(bps_data$modelers, 
               caption = "Model developers and reviewers")
} else {
  cat("No modeler information available")
}
```

### Reference Conditions

```{r reference-conditions}
if (nrow(bps_data$reference_conditions) > 0) {
  knitr::kable(bps_data$reference_conditions, 
               caption = "Reference condition data")
} else {
  cat("No reference condition data available")
}
```

## Detailed Descriptions

```{r descriptions}
if (nrow(bps_data$text_data) > 0) {
  text_info <- bps_data$text_data[1, ]
  
  cat("### Vegetation Type\n")
  cat(text_info$vegetation_type, "\n\n")
  
  cat("### Geographic Range\n") 
  cat(text_info$geographic_range, "\n\n")
  
  cat("### Vegetation Description\n")
  cat(text_info$vegetation_description, "\n\n")
  
  cat("### Disturbance Description\n")
  cat(text_info$disturbance_description, "\n\n")
} else {
  cat("No detailed description data available")
}
```

```{r cleanup, include=FALSE}
# Close database connection
dbDisconnect(con)
```

---

*Report generated on `r Sys.time()` from BPS Database*
